\documentclass[12pt, std]{article}
\usepackage{amssymb}
\begin{document}

\begin{center} \textbf{Practice Exercises.} \end{center}

\

Assume throughout that we are working
with Hausdorff spaces.

\

Exercise 1. Find an infinite and bounded set in the Sorgenfrey Line with no
limit point.  Show that this set is not compact.

\

Exercise 2. Suppose that $M$ is a closed set and that every infinite
subset of $M$ has a limit point.  Show that if $M$ has a finite set
of limit points then it is compact.  [Hint: do the case where $M$
has only one limit point first.]

\

Exercise 3.  Show that if $A$ and $B$ are compact then $A \cup B$
and $A \cap B$ are compact.  

\

Exercise 4.  Suppose that $M$ is a compact subset of the reals. Then
$M$ is bounded and contains its least upper bound.

\

Exercise 5.  Give an example of a set $M \subset X$ that is not
compact and a continuous function $f: X \rightarrow Y$ so that $f(M)$ is
compact.

[Hint: this can be done with subsets of the reals.  Draw the graph of the function.]

\

Exercise 6. Give an example of an infinite subset $M$ of the
reals so that: $M$ is bounded and contains its least upper bound, and every subset of $M$ contains its greatest lower bound.

\

I. Give an example of such a set with infinitely many limit points.

II. Show that any such $M$ is compact.

\


Exercise 7.  Consider the Reals $\mathbb{R}$; use theorem 7.3 to prove the following.

\

\qquad 1.  The reals is uncountable.


\qquad 2.  The unit interval is not the union of countably many
Cantor sets.

\qquad 3.  Suppose that for each integer $i$, $U_i$ is open in $\mathbb{R}$ and is dense in $\mathbb{R}$.   Then $\cap_{i=1}^\infty U_i \ne \emptyset$.  [Hint: in fact  $[0,1] \cap (\cap_{i=1}^\infty U_i) \ne \emptyset$.]

\newpage

Exercise 8.  Suppose that $X$ is a metric space.

\qquad A. Show that if $x \in X$ then $\{B_{\frac 1n}(x) | n \in \mathbb{N} \}$ is a local basis at $x$.

\qquad B. Show that $X$ is completely separable.

\qquad C. Show that $X$ is separable.

\

Exercise 9A. Suppose $f: M \to X$ is continuous and $M$ is a compact space.  Prove that $f(M) = \{ f(m) | m \in M \}$ is compact.

Exercise 9B. Suppose $f: M \to X$ is continuous and $M$ is a connected space.  Prove that $f(M) = \{ f(m) | m \in M \}$ is connected.

\

Exercise 10.  Show that every infinite subset of a compact set has a limit point.

\

Exercise 11  Prove that if $M$ is a nowhere dense subset of $X$ then every subset of $M$
is also nowhere dense in $X$.


\

Exercise 12.  Prove that if $M$ is a non-degenerate connected set and $p \in M$ then $p$
is a limit point of $M$.

\

Exercise 13.  Suppose that $X$ is a metric space with metric $d$ and $H$ and $K$ are disjoint compact subsets of $X$.  Show that there is a number $\epsilon > 0$ so that $d(h, k) > \epsilon$ for all $h \in H, k \in K$.

\

Exercise 13B.  Find two disjoint closed sets $H$ and $K$ in the plane $\mathbb{E}^2$ so that if $\epsilon > 0$ there are points $h \in H$ and $k \in K$ so that $d(h, k) < \epsilon$.

\

Exercise 14.  Suppose that $X$ is a metric space with metric $d$ and $p \in X$.  Define the function $f: X \to \mathbb{R}$ by $f(x) = d(x,p)$.  Show that $f$ is continuous.

\

Exercise 15.  Prove that the Hausdorff space $X$ is regular if and only if for each $p \in X$ and open set $U$ containing $p$ there is an open set $V$ containing $p$ so that $p \in V \subset \overline{V} \subset U$.


\end{document}
