\documentclass[12pt, std]{article}
\usepackage{amssymb}
\begin{document}

\begin{center} \textbf{Connectedness.} \end{center}

\

Definition.  The sets $H$ and $K$ are said to be \textit{mutually
separated} if and only if neither contains a point or a limit point
of the other.

\

Definition.  The set $M$ is said to be \textit{connected} if and
only if it is not the union of two non-empty mutually separated
sets.

\

Theorem 6.1.  If $M$ is connected then $\overline{M}$ is connected.

\

Theorem 6.2.  Suppose that $U$ and $V$ are disjoint open sets and
the connected set $M$ is such that $M\subset U \cup V$.  Then either
$M \subset U$ or $M \subset V$.

\

Theorem 6.3.  If $M$ is compact and not connected, then $M$ is the
union of two disjoint closed (non-empty) sets.

\

Theorem 6.4.  Suppose that $G$ is a collection of connected sets and
that there is a point $p$ that lies in every element of $G$.  Then
$\cup G$ is connected.

\

Theorem 6.5.  Suppose that $f: X \rightarrow Y$ is a continuous
function and $M$ is a connected subset of $X$.  Then $f(M)$ is
connected.

\

Theorem 6.6.  Suppose that $M$ is connected, $U$ is an open set and
$M$ contains a point in $U$ and a point that is not in $U$.  Then $M
\cap Bd(U) \ne \emptyset$.

\

Exercise 6.7.  

\qquad a. The real line is connected.

\qquad b. The Sorgentry line is not connected.

\qquad c. The square disc $[0,1] \times [0,1]$ with the dictionary order topology is connected.  Comment: this is true whether or not you include the first and last points.

\

Definition.  If $M$ is a set and $p\in M$, then the component of $M$
containing $p$ is the set to which $x$ belongs if and only if a
connected subset of $M$ contains both $p$ and $x$.

\

Theorem 6.8.  Let $M \subset X$ be a pointset.  Then the relation $x
\sim p$ defined by $x \sim p$ iff $x$ is in the component of $M$
containing $p$ is an equivalence relation.

\

Theorem 6.9. If $C$ is the component of the the set $M$. Then $C$ is
a maximal connected subset of $M$.  [This means that 1. $C$ is
connected and 2. $C$ is not a proper subset of any connected subset
of $M$.]

















\end{document}
